Fossil-calibrated phylogeny of Onagraceae: patterns of floral and chromosome evolution

### 2014-04-28 manuscript.tex
character state recon. started

>>>>

\paragraph{Character state reconstruction}
I scored six characters, including
chromosome number, floral merosity, petal color, and self-compatibility/incompatibility. 
Character data was assembled from the comprehensive \citet{wagner2007revised} Onagraceae monograph.
Ancestral character state reconstructions of petal number and petal color were performed using Mesquite v2.75 \citep{mesquite}.
Characters were treated as unordered categorical data, and optimized using maximum likelihood
under the Markov k-state 1 parameter (Mk1) model \citep{lewis2001likelihood}.
